Joe Biden Predicted to Win 59% of the Popular Vote in the 2024 U.S. Presidential Election

### 2024-03-15 paper/paper.qmd
c

---
title: "Joe Biden Predicted to Win 59% of the Popular Vote in the 2024 U.S. Presidential Election"
subtitle: "A 2024 U.S. Election Forecast Using Multi-Level Regression with Post-Stratification (MRP)"
author: 
  - Talia Fabregas
  - Fatimah Yunusa
thanks: "Code and data are available at: https://github.com/taliafabs/US-Election-Forecast-2024.git"
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election will take place on November 5th and it will be a rematch between President Joe Biden and Former President Donald Trump. Using multi-level regression with post-stratification (MRP) we found that ... Based on our results, we can predict that Joe Biden will win 59% of the popular vote. "
format: pdf
number-sections: true
bibliography: references.bib
---

@@

biden_ec_lower<- sum(biden_states_mean$electoral_votes)
trump_ec_lower <- sum(trump_states_mean$electoral_votes)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| #| label: tbl-popvotepost
#| tbl-cap: "Estimated Popular Vote"
biden_support_overall <- presidential_vote_model %>%
  add_epred_draws(newdata = poststrat_data_cells) %>%
  rename(support_biden_predict = .epred) %>%
  mutate(support_biden_predict_prop = support_biden_predict * prop) %>%
  ungroup() %>%
  summarise(
    "Lower Estimate" = quantile(support_biden_predict, 0.05),
    "Mean Estimate" = mean(support_biden_predict),
    "Upper Estimate" = quantile(support_biden_predict, 0.95)
  )

@@

>>>>

---
title: "Joe Biden Predicted to Win 59% of the Popular Vote in the 2024 U.S. Presidential Election"
subtitle: "A 2024 U.S. Election Forecast Using Multi-Level Regression with Post-Stratification (MRP)"
author: 
  - Talia Fabregas
  - Fatimah Yunusa
thanks: "Code and data are available at: https://github.com/taliafabs/US-Election-Forecast-2024.git"
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election will take place on November 5th and it will be a rematch between President Joe Biden and Former President Donald Trump. Using multi-level regression with post-stratification (MRP) we found that ... Based on our results, we can predict that Joe Biden will win 59.39% of the popular vote. "
format: pdf
number-sections: true
bibliography: references.bib
---

@@

biden_ec_lower<- sum(biden_states_mean$electoral_votes)
trump_ec_lower <- sum(trump_states_mean$electoral_votes)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| label: tbl-popvotepost
#| tbl-cap: "Biden Estimated Popular Vote %"

props <- poststrat_analysis_data %>%
  group_by(state, races, age_bracket, sex, education_level, urban) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  group_by(state) %>%
  mutate(prop = n / sum(n))

@@

# need to fix this
biden_support_overall <- presidential_vote_model %>%
  add_epred_draws(newdata = poststrat_data_cells) %>%
  rename(support_biden_predict = .epred) %>%
  mutate(support_biden_predict_prop = support_biden_predict * prop) %>%
  ungroup() %>%
  summarise(
    "Lower Estimate" = round(quantile(support_biden_predict, 0.05) * 100,2),
    "Mean Estimate" = round(mean(support_biden_predict) * 100, 2),
    "Upper Estimate" = round(quantile(support_biden_predict, 0.95) * 100,2)
  )

```{r}
#| eval: true
#| echo: false
#| warning: false
#| label: tbl-supporttbl
#| tbl-cap: "Estimates for support for Biden in each state"
